TOI based ProVisioNet

### 2021-09-10 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNet_ET_EVENTS_01_01_TOI-based_data.Rmd
update TOI classes

df_MK_02 <- read_tsv(file = "data/02_02_MK_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")
```

@@

@@

# AP Duration TOI
for (i in TOI_names) {

@@

# MK Duration TOI
for (i in TOI_names) {

@@

df_cappa_dur$Duration_of_interval_AP_01 <- round(df_cappa_dur$Duration_of_interval_AP_01/1000,
                                              digits = 2
                                              )

df_cappa_dur$Duration_of_interval_MK_01 <- round(df_cappa_dur$Duration_of_interval_MK_01/1000,
                                              digits = 2
                                              )

@@

df_cappa_dur$TOI_class[df_cappa_dur$TOI == "Head_on_table" |
                         df_cappa_dur$TOI == "Looking_at_phone" |
                         df_cappa_dur$TOI == "Drawing"] <- "lack_of_eagerness"

@@

df_cappa_dur_aggr <- df_cappa_dur %>%
  group_by(TOI_class) %>%
  summarise(Duration_mean_AP = mean(Duration_of_interval_AP_01),
            Duration_mean_MK = mean(Duration_of_interval_MK_01)
            )

>>>>

# df_MK_02 <- read_tsv(file = "data/02_02_MK_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")

df_AP_04 <- read_tsv(file = "data/04_04_AP_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")

df_MK_04 <- read_tsv(file = "data/04_04_MK_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")

@@

# df_AP_02 <- df_AP_02 %>% 
#   select(TOI, Duration_of_interval)
# 
# df_MK_02 <- df_MK_02 %>% 
#   select(TOI, Duration_of_interval)

df_AP_04 <- df_AP_04 %>% 
  select(TOI, Duration_of_interval)

df_MK_04 <- df_MK_04 %>% 
  select(TOI, Duration_of_interval)

@@

# AP_01 Duration TOI
for (i in TOI_names) {

@@

# MK_01 Duration TOI
for (i in TOI_names) {

@@

# AP_04 Duration TOI
for (i in TOI_names) {

  val <- df_AP_04$Duration_of_interval[df_AP_04 == i]

  df_cappa_dur$Duration_of_interval_AP_04[df_cappa_dur$TOI == i] <- val
}

# MK_04 Duration TOI
for (i in TOI_names) {

  val <- df_MK_04$Duration_of_interval[df_MK_04 == i]

  df_cappa_dur$Duration_of_interval_MK_04[df_cappa_dur$TOI == i] <- val
}

@@

df_cappa_dur$TOI_class[df_cappa_dur$TOI == "Head_on_table" |
                         df_cappa_dur$TOI == "Looking_at_phone" |
                         df_cappa_dur$TOI == "Drawing"] <- "Lack_of_eagerness"

@@

df_cappa_dur_aggr <- df_cappa_dur %>%
  group_by(TOI_class) %>%
  summarise(Duration_mean_AP_01 = mean(Duration_of_interval_AP_01),
            Duration_mean_MK_01 = mean(Duration_of_interval_MK_01),
            Duration_mean_AP_04 = mean(Duration_of_interval_AP_04),
            Duration_mean_MK_04 = mean(Duration_of_interval_MK_04)
            )

df_cappa_dur_aggr$Duration_mean_AP_01 <- round(df_cappa_dur_aggr$Duration_mean_AP_01/1000,
                                              digits = 2
                                              )

df_cappa_dur_aggr$Duration_mean_MK_01 <- round(df_cappa_dur_aggr$Duration_mean_MK_01/1000,
                                              digits = 2
                                              )

df_cappa_dur_aggr$Duration_mean_AP_04 <- round(df_cappa_dur_aggr$Duration_mean_AP_04/1000,
                                              digits = 2
                                              )

df_cappa_dur_aggr$Duration_mean_MK_04 <- round(df_cappa_dur_aggr$Duration_mean_MK_04/1000,
                                              digits = 2
                                              )
